Sound Automated Synthesis of Digital Controllers

### 2016-10-13 paper/paper.tex
revised sec 4.1

The design of our synthesiser is given in Fig.~\ref{fig:CEGIS} and
consists of two phases, {\sc Synthesise} and {\sc Verify}, which
interact via a finite set of test vectors {\sc inputs} that is updated
incrementally.  Given the aforementioned specification $\sigma$, the
{\sc synth} procedure tries to find an existential witness $\vec{P}$
satisfying the specification $\sigma(\vec{x}, \vec{P})$ for all
$\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
%
If {\sc synthesise} succeeds in finding an witness $\vec{P}$, this
witness is a candidate solution to the full synthesis formula. 
We pass this candidate solution to {\sc verify}, which 
checks whether it is a full solution.
%determines whether
%it does satisfy the specification on all inputs by checking
%satisfiability of the following verification formula:
%
%$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
%If this formula is unsatisfiable, 
%% the candidate solution is in fact a 
%% full solution.
If this is the case, then
the algorithm terminates.
Otherwise, additional information is provided to the {\sc synthesise}
phase (e.g. a new counterexample that is added to the {\sc inputs} set)
and the loop iterates again.

@@

%% It is
%% worth noting that each iteration of the loop adds a new input to the
%% finite set $\text{\sc inputs}$ being used for synthesis.  Given that
%% the full set of inputs $\mathcal{D}$
%% %\blue{[which by now should have a name, as suggested to be introduced above]} 
%% is finite, this means that the refinement loop
%% can only iterate a finite number of times.

@@

\begin{table}[H]
\centering
\begin{tabular}{c l | r l}
Plant & Benchmark                  & Time    & \\\cline{1-3}
$G_1$ & CruiseControl02            & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  & 46\,s   & \\
$G_2$ & SpringMassDamper           & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
$G_3$ & SatelliteB2                & 7\,s    & \\
$G_3$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
$G_3$ & SatelliteC2                & 2\,s    & \\
$G_3$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
      & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
      & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
      & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
      & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
      & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
      & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
      & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
\end{tabular}

>>>>

The design of our synthesiser is given in Fig.~\ref{fig:CEGIS} and
consists of two phases, {\sc Synthesise} and {\sc Verify}, which
interact via a finite set of test vectors {\sc inputs} that is updated
incrementally.  Given the aforementioned specification $\sigma$, the
{\sc synth} procedure tries to find an existential witness $\vec{P}$
satisfying the specification $\sigma(\vec{x}, \vec{P})$ for all
$\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$).
%
If {\sc synthesise} succeeds in finding an witness $\vec{P}$, this
witness is a candidate solution to the full synthesis formula. 
We pass this candidate solution to {\sc verify}, which 
checks whether it is a full solution ({\it i.e.}, $\vec{P}$
satisfies the specification $\sigma(\vec{x}, \vec{P})$ for all
$\vec{x}\in\mathcal{D}$).
%determines whether
%it does satisfy the specification on all inputs by checking
%satisfiability of the following verification formula:
%
%$\exists \vec{x} . \lnot \sigma(\vec{x}, \vec{P})$
%If this formula is unsatisfiable, 
%% the candidate solution is in fact a 
%% full solution.
If this is the case, then the algorithm terminates.
Otherwise, additional information is provided to the {\sc synthesise}
phase in the form of a new counterexample that is added to the {\sc inputs} set
and the loop iterates again (note that, for now, we ignore the 
second feedback signal ``Increase Precision'' provided by the {\sc Verify}
phase in Fig.~\ref{fig:CEGIS} as it is specific to control synthesis and will 
be described in the next section).

@@

It is
worth noting that each iteration of the loop adds a new input to the
finite set $\text{\sc inputs}$ being used for synthesis.  Given that
the full set of inputs $\mathcal{D}$
%\blue{[which by now should have a name, as suggested to be introduced above]} 
is finite, this means that the refinement loop
can only iterate a finite number of times.

@@

\begin{table}[H]
\centering
\begin{tabular}{c l | r l}
      & Benchmark                  & Base    & \\\cline{1-2}
$G_1$ & CruiseControl02            & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  & 46\,s   & \\
$G_2$ & SpringMassDamper           & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ & \xmark  & \\
$G_2$ & SatelliteB2                & 7\,s    & \\
$G_2$ & SatelliteB2$^\dagger$      & 6601\,s & \tbmark\\
$G_2$ & SatelliteC2                & 2\,s    & \\
$G_2$ & SatelliteC2$^\dagger$      & 76\,s   & \tbmark\\
      & a\_PL1\_SCH2\_IMPL1        & 2704\,s & \\
      & a\_PL1\_SCH2\_IMPL2        & 538\,s  & \\
      & a\_PL1\_SCH2\_IMPL3        & 12\,s   & \\
      & a\_PL1\_SCH3\_IMPL1        & 318\,s  & \\
      & a\_PL1\_SCH3\_IMPL2        & 967\,s  & \\
      & a\_PL1\_SCH3\_IMPL3        & 9798\,s & \\
      & a\_PL1\_SCH4\_IMPL1        & 6304\,s & \\
\end{tabular}
